% Chapter 4: Artificial Intelligence Features
\chapter{Artificial Intelligence Features}

\chapterquote{Artificial intelligence is the new electricity.}{Andrew Ng}

\section*{Introduction}
\addcontentsline{toc}{section}{Introduction}

This chapter explores the integration of artificial intelligence capabilities within our real estate platform. We have developed four distinct AI models, each addressing specific needs within the ecosystem. These models collectively enhance user experience, improve decision-making processes, and provide valuable insights to various stakeholders in the real estate market.

The AI features presented in this chapter represent a significant competitive advantage for our platform, enabling more accurate property valuations, personalized recommendations, intelligent assistance, and efficient administrative operations. Each model has been carefully designed to solve real-world challenges faced by users interacting with real estate data and transactions.

\section{AI Development Overview}
\subsection{Technology Stack}


\subsection{Data Preprocessing Pipeline}
\subsubsection{Feature Engineering}


\subsubsection{Dataset Creation}


\subsection{Knowledge Base Construction}
\subsubsection{Information Extraction}


\subsubsection{Knowledge Organization}

\section{Property Valuation Prediction Model}
\subsection{Overview and Objectives}
The property valuation prediction model is designed to estimate both the market value and potential rental income for real estate properties. This provides investors with crucial information to make informed investment decisions.

\subsection{Model Architecture and Training Process}
\subsubsection{Model Selection}
After evaluating multiple approaches, we implemented:


\subsubsection{Training Methodology}


\subsection{Prediction Capabilities}


\subsection{Performance Metrics and Evaluation}


\subsection{Integration with Property Listings}
\subsection{Limitations and Future Improvements}

\section{Real Estate Assistant}
\subsection{Purpose and Capabilities}
\subsection{Conversational Interface Design}
\subsection{Legal Advisory Capabilities}
\subsection{Investment Insights Generation}
\subsection{Interaction Design and User Experience}
\subsection{Compliance and Information Accuracy}

\section{Role-Based Backoffice Agent}
\subsection{System Architecture}
\subsection{Database Integration and Access Control}
\subsection{Role-Based Permission Framework}
\subsection{Query Processing Pipeline}
\subsection{Response Generation and Formatting}
\subsection{Security and Privacy Considerations}

\section{Investor-Focused Recommendation System}
\subsection{Recommendation Algorithm Design}
\subsection{User Profiling and Preference Learning}
\subsection{Investment Criteria Matching}
\subsection{Integration with Mobile Platform}
\subsection{Performance Evaluation}
\subsection{Personalization and Adaptation Mechanisms}





