\chapter{Conclusion \& Future Work}

\chapterquote{The best way to predict the future is to create it.}{Abraham Lincoln}

This project successfully delivered \textbf{\textcolor{primary}{Korpor}}, a revolutionary \textbf{AI} and \textbf{blockchain}-powered real estate investment platform that transforms how investors and agencies interact in the digital marketplace. Through comprehensive development using modern technologies and \textbf{agile} methodologies, we have created a secure, intelligent, and user-friendly ecosystem that addresses the key challenges of traditional real estate investment.

\section{Key Achievements}

\textbf{\textcolor{primary}{Korpor}} represents a significant advancement in real estate technology, delivering several core innovations:

\begin{itemize}
    \item \textbf{AI-Powered Intelligence}: Successfully implemented \textbf{machine learning} algorithms for personalized property recommendations, price predictions, and intelligent \textbf{chatbot} assistance, enhancing investor decision-making capabilities.
    
    \item \textbf{Blockchain Security}: Integrated \textbf{Solidity} smart contracts on the \textbf{Sepolia testnet} with \textbf{Infura} infrastructure, ensuring transparent, immutable, and secure transaction recording for all investment activities.
    
    \item \textbf{Dual-Interface Platform}: Delivered both a comprehensive \textbf{React Native} mobile application for investors and a sophisticated web dashboard for administrators and real estate agencies, enabling seamless property management, user oversight, and business analytics across all devices.
    
    \item \textbf{Scalable Architecture}: Implemented a robust \textbf{microservices} architecture on \textbf{Google Cloud Platform} with \textbf{Cloud Run} deployment, ensuring high availability and performance scalability.
    
    \item \textbf{Multi-Actor Ecosystem}: Created role-based access controls serving Super Admins, Company Admins, Real Estate Agents, and Investors, each with tailored functionality and responsibilities.
\end{itemize}

\section{Technical Excellence}

The platform demonstrates technical sophistication through its integration of cutting-edge technologies including \textbf{Express.js} backend services, \textbf{React}-based web dashboard, \textbf{Cloud SQL} database management, \textbf{TanStack} for state management, and \textbf{Clerk} for secure authentication. The dual-interface architecture serves both mobile investors and web-based administrators with optimized user experiences, while automated testing with \textbf{playwright} and comprehensive \textbf{CI/CD} pipelines through \textbf{GitHub} ensures code quality and reliable deployments.

\section{Impact and Value}

\textbf{\textcolor{primary}{Korpor}} successfully bridges the gap between traditional real estate investment and modern digital finance, offering agencies expanded market reach and operational efficiency through its comprehensive web dashboard, while providing investors with accessible, transparent, and secure investment opportunities via the mobile application. The platform's \textbf{AI}-driven insights and \textbf{blockchain}-secured transactions create unprecedented trust and intelligence in real estate investment decisions across both interfaces.

\section{Future Enhancements}

The platform's modular architecture positions it for continuous evolution, with planned enhancements including advanced \textbf{predictive analytics}, automated portfolio rebalancing, integration with external financial planning tools, and expansion to additional \textbf{blockchain} networks for broader market access.

\textbf{\textcolor{primary}{Korpor}} stands as a testament to the transformative power of combining \textbf{artificial intelligence}, \textbf{blockchain} technology, and user-centric design in creating the next generation of \textbf{financial technology} solutions.

% End page numbering after last chapter
\clearpage
\pagenumbering{gobble} % Remove page numbers from here onwards